Domestic cooking and likelihood

### 2022-07-01 inst/cook.Rmd
use sticker in Rmd
labels and cache

```{r}
maxp(H)
```

@@

```{r maxlike, echo=FALSE}
dotchart(maxp(H),pch=16,main="probabilities")
dotchart(log(maxp(H)),pch=16,main="log probabilities")
```

@@

```{r}
equalp.test(H)
```

@@

```{r}
samep.test(H,c("p1","p2"))
```

@@

```{r}
library(partitions)
M <- perms(5)
M[] <- paste("p",M,sep="")
imH <- indep(maxp(H))
f <- function(o){loglik(imH,race(o),log=FALSE)}
LL <- apply(perms(5),2,f)
length(LL)
sum(LL)
head(LL)
```

@@

```{r}
obs <- c(5,4,3,2,1)
(pval <- sum(LL[LL <= f(obs)])/sum(LL))
```

@@

## Changes in cooking strength.

@@

```{r,beforetraining}
# observations before training:
Hbefore <- 
  race(c("p5","p2","p3","p4","p1")) + #  5 is the best, 4 the worst.
  race(c("p5","p3","p2","p4","p1")) + #  5 is the best, 1 the worst.
  race(c("p4","p5","p3","p2","p1")) + #  4 is the best, 1 the worst.
  race(c("p5","p3","p4","p1","p2")) + #  5 is the best, 2 the worst.
  race(c("p2","p5","p3","p1","p4"))   #  2 is the best, 4 the worst.
Hbefore
```

@@

```{r,addbeforeandafter}
maxp(Hbefore+Hafter)
```

@@

```{r,testnullzerotrainingeffect}
specificp.gt.test(Hbefore+Hafter, "S", 0)
```

>>>>

```{r,label=maxH,cache=TRUE}
maxp(H)
```

@@

```{r maxlike, echo=FALSE,cache=TRUE}
dotchart(maxp(H),pch=16,main="probabilities")
dotchart(log(maxp(H)),pch=16,main="log probabilities")
```

@@

```{r,equaltest,cache=TRUE}
equalp.test(H)
```

@@

```{r,samtest,cache=TRUE}
samep.test(H,c("p1","p2"))
```

@@

```{r,label=obscons,cache=TRUE}
library(partitions)
M <- perms(5)
M[] <- paste("p",M,sep="")
imH <- indep(maxp(H))
f <- function(o){loglik(imH,race(o),log=FALSE)}
LL <- apply(perms(5),2,f)
length(LL)
sum(LL)
head(LL)
```

@@

```{r,label=obspv}
obs <- c(5,4,3,2,1)
(pval <- sum(LL[LL <= f(obs)])/sum(LL))
```

@@

## Changes in cooking strength

@@

```{r,label=beforetraining,cache=TRUE}
# observations before training:
Hbefore <- 
  race(c("p5","p2","p3","p4","p1")) + #  5 is the best, 4 the worst.
  race(c("p5","p3","p2","p4","p1")) + #  5 is the best, 1 the worst.
  race(c("p4","p5","p3","p2","p1")) + #  4 is the best, 1 the worst.
  race(c("p5","p3","p4","p1","p2")) + #  5 is the best, 2 the worst.
  race(c("p2","p5","p3","p1","p4"))   #  2 is the best, 4 the worst.
Hbefore
```

@@

```{r,addbeforeandafter,cache=TRUE}
maxp(Hbefore+Hafter)
```

@@

```{r,testnullzerotrainingeffect,cache=TRUE}
specificp.gt.test(Hbefore+Hafter, "S", 0)
```
